Secure Composition of Robust and Optimising Compilers

### 2023-07-08 popl/main.tex
RelWork CCT

>>>>

The approach to cryptographic constant time in this paper is high--level, where a programming language exposes a way to switch the semantics to a data (operand) independent timing mode.
Since identifiers in $\Lscct$ are annotated with a secrecy tag, this approach is similar to others with information flow control.
For example, Vale~\cite{bond2017vale} uses Dafny to ensure constant--time assembly code, while Jasmin~\cite{almeida2017jasmin} makes use of the Coq proof assistant to reject non--constant--time programs.
CT-Wasm~\cite{watt2019ctwasm} enforces constant--timeness by means of a type system.
Different to the approach of this paper, these approaches necessitate that the programmer writes \gls{cct} code.
An approach to allow programmers to write more high--level code is CryptOpt~\cite{kuepper2023cryptopt}, which generates efficient target-code by means of a randomized search.
This paper abstracts over concrete mitigation strategies and simply assumes that there is a flag to switch to a cryptographic--constant time execution mode.
This can be realized by employing the FaCT~\cite{cauligi2019fact} compiler, which translates common non-constant time code patterns to be constant--time, and the data (object) independent timing execution mode of modern processors.
